1-intro

### 2022-02-04 1-intro.Rmd
section division

The rest of the paper will be divided as follows: [complete when the paper structure is more solid]

<!-- Section 2 reviews the existing data structure for spatio, temporal, and spatio-temporal data. Section 3 presents a new data structure for spatio-temporal data: cubble. Then the paper introduces the workflow of data manipulation and visualisation with the cubble structure in Section 4. Section 5 gives some examples on how common spatial and temporal manipulations are performed with cubble and how static and interactive visualisation help to understand climate and [...] data. \newline -->

>>>>

The rest of the paper will be divided as follows: Section 2 presents the workflow of data manipulation in cubble. Section 3 explains how cubble deals with some advanced considerations  including data with hierarchical structure, data matching, and how cubble fits with existing static and interactive visualisation tools. Section 4 gives examples of the features introduced in the previous two sections with climate and hydrology data. An example on how cubble handle Netcdf data is also provided. Section 5 concludes the paper
